---
title: "Saccoloma Leaf Age @ La Selva 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Methods


##Site and Species Surveys

This study was located at La Selva Biological Research Station in Heredia, Costa Rica (84⁰00’12W, 10⁰25’52N). This site is a 600 hectare wet tropical forest, with elevation ranging from 35-137m above sea level. The site receives 4m of annual rainfall with a moderate dry season. Annual mean temperatures fluctuates between between 24-27⁰C, while daily temperatures can fluctuate up to 12⁰C (McDade et al. 1994). At least once per year (Diedra personnal communication) newly formed pinnae of Saccoloma spp were color tagged according to year. Pinnae generally lasted from 3-4 years, with dissappearance mostly occuring from stem fall distubance. 

A survey of physiological and stoichiometric parameters was conducted for x individuals of. We surveyed in situ gas exchange during mid-morning hours. For leaf gas exchange measurements, a LiCor 6400 portable photosynthesis system (LiCor BioSciences) was used with the standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes. The CO2 mixer  was set to 400 μmol·m-2·sec-1 and leaf temperature was maintained at 30℃. Gas exchange parameters were logged once CO2 and water vapor fluxes were stable. Net photosynthetic rate (An) and stomatal conductance (gs) were logged at a standard photosynthetic photon flux density (PPFD) level of 500 μmol·m-2·sec-1,which has been previously shown to produce maximum photosynthetic rates for understory terrestrial plants (Watkins et al 2010).


Foliar tissue was collected following gas exchange measurements and used for nutrient analyses. Samples were dried to a constant mass and ground to a powder. Carbon and nitrogen analyses were measured using a Cornell machine, with the percentage of carbon and nitrogen in samples calculated by comparison with certified standards.
 
Photosynthetic nitrogen use efficiency (PNUE) was defined as the ratio of photosynthesis to leaf N content on a mass basis.


##Chlorophyll Content

For each Selaginella species, subsamples of fresh foliar tissue used during gas exchange measurements were used to calculate chlorophyll content (Chl). Get specs for cholorpphyll from Yarmilla


```{r format sacc, echo=FALSE}
chlro <- read.csv("sacc_chl.csv")
photo <- read.csv("sacc_photo.csv")

addleafage_func <- function(x){
  x$leafage <- ifelse(x$Color == "w", 1, 99)
  x$leafage <- ifelse(x$Color == "o", 2, x$leafage)
  x$leafage <- ifelse(x$Color == "y", 3, x$leafage)
  x$leafage <- ifelse(x$Color == "p", 4, x$leafage)
return(x)
  }

chlro <- addleafage_func(chlro)
photo <- addleafage_func(photo)

library(doBy)
photo_agg <- summaryBy(Photo + Cond + Ci + Trmmol ~ Indiv + leafage, data=photo,
                       FUN=mean, keep.names = TRUE)

  photo_agg$iwue <- with(photo_agg, Photo/Trmmol)

photo_agg2 <- photo_agg[!photo_agg$Indiv == 26, ]    
  
cols <- c("white", "darkorange3", "yellow", "purple4")
years <- c("Year 1", "Year 2", "Year 3", "Year 4")

```

## Summary

Here we measured gas exchange and chlorophyll content on different age classes of Saccoloma at La Selva. Each individual (n=25) had fronds with ages classes of 1 to 4 years. Below are the boxplots (excluding outliers) of photosynthesis (A~n~), stomatal conductance (g~s~), instantaneous water use efficiency (ITE), transpiration (E~l~) and chlorophyll content. Gas exchange was performed on a subset of individuals (n=10). For clarity I have colored the age classes in the manner they are marked in the field.

There is an issue with Year 2 & 3 gas exchange data from #26 . Something went wrong on the water side of gas exchange, although A~n~ looks alright.  I have deleted it for the moment. I have pasted the raw data that was deleted at the bottom so you can have a look.

```{r gas exchange, echo=FALSE, fig.align='center',fig.width = 5, fig.height = 7}
boxplot(Photo ~ leafage, data=photo_agg2, outline=FALSE, col=cols,xaxt='n',
        ylab=expression(italic(A)[net]~~(mu*mol~m^-2~s^-1)))
axis(1, at=1:3, years[1:3])

boxplot(Cond ~ leafage, data=photo_agg2, outline=FALSE, col=cols,xaxt='n',
        ylab=expression(g[s]~~(mu*mol~m^-2~s^-1)))
axis(1, at=1:3, years[1:3])
```
A~n~ seems to be higher in year 2 but there is  a lot of variation within other years. Stomatal conductance may be higher in year 3, despite a ton of variation in year 2. Ill run some stats sonon.


```{r iwue, echo=FALSE, fig.align='center',fig.width = 5, fig.height = 7}
boxplot(iwue ~ leafage, data=photo_agg2, outline=FALSE, col=cols,xaxt='n',
        ylab=expression(ITE~~(mmol~CO[2]~mol~H[2]*O^-1)))
axis(1, at=1:3, years[1:3])
boxplot(Trmmol ~ leafage, data=photo_agg2, outline=FALSE, col=cols,xaxt='n',
        ylab=expression(italic(E)[L]~~(mmol~m^-2~s^-1)))
axis(1, at=1:3, years[1:3])
```
Instantaneous water use efficiency looks like it declines in year 3. Looks to be mostly driven by water loss instead of A~n~

```{r chl, echo=FALSE, fig.align='center',fig.width = 5, fig.height = 5}
boxplot(chl ~ leafage, data=chlro, outline=FALSE, col=cols, xaxt='n',
         ylab="cholorphyll content  (units)")
axis(1, at=1:4, years)
```
No obvious changes in chlorophyll content. It will be interesting to see what happens with leaf nitrogen.

### Transpiration data is bad for certain ages for #26
```{r baddat,}
photo[photo$Indiv == 26, c("Indiv", "leafage", "Photo", "Cond", "Trmmol", "Ci")] 