---
title: Saccoloma inaequale
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: tree-physiology.csl
bibliography: references.bib
---

\
Courtney E. Campany^1^, Christopher Krieg^2^, James E. Watkins Jr.^1^ 

\
^1^ Department of Biology, Colgate University, Hamilton, NY, USA
\
^2^ Department of Biology, University of Florida, Gainesville, Fl, USA

\
Corresponding author: 

\
Key Words: 



```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')
```

```{r loaddata, echo=FALSE}
alldata <- read.csv("calculated_data/alldata.csv")
alldata_no26 <- alldata[!alldata$Indiv == 26,]
source("plot_objects.R")
photo <- read.csv("raw_data/sacc_photo.csv")
```

# Abstract

/
Key Words: 

# Introduction

# Methods

##Site and species surveys

This study was located at La Selva Biological Research Station in Heredia, Costa Rica (84&deg;00’12W, 10&deg;25’52N). This site is a 600 hectare wet tropical forest, with elevation ranging from 35-137m above sea level. The site receives 4m of annual rainfall with a moderate dry season. Annual mean temperatures fluctuates between between 24-27 &deg;C, while daily temperatures can fluctuate up to 12 &deg;C [@mcdade_selva_1994]. 

\

At least once per year (insert methods from Diedra) newly formed fronds of *Saccoloma inaequale* (n = ?) were color tagged according to year. Fronds generally lasted from 3-4 years, with dissappearance mostly occuring from stem fall distubance. 

## Physiological measurements

A survey of physiological and stoichiometric parameters was conducted on all present age classes of fronds for a subset of 10 *S. inaequale* individuals. For leaf gas exchange measurements, a LiCor 6400 portable photosynthesis system (LiCor BioSciences) was used with the standard leaf chamber (2 x 3 cm) equipped with blue-red light emitting diodes. The CO~2~ mixer  was set to 400 μmol m^-2^ sec^-1^ and leaf temperature was maintained at 25 &deg;C. Gas exchange parameters were logged once CO~2~ and water vapor fluxes were stable. Net photosynthetic rate (An) and stomatal conductance (g~s~) were logged at a standard photosynthetic photon flux density (PPFD) level of 500 $\mu$mol m^-2^ s^-1^,which has been previously shown to produce maximum photosynthetic rates for tropical understory terrestrial plants [@watkins_hydraulic_2010]. All in situ gas exchange measurements were conducted during mid-morning hours. 

## Leaf chemistry

Foliar tissue was collected following gas exchange measurements and used for nutrient and istopte analyses. Samples were dried to a constant mass and ground to a powder. Foliar $\delta$^13^C, carbon content and nitrogen content were measured using a Thermo Delta V isotope ratio mass spectrometer interfaced to a NC2500 elemental analyzer. The percentage of carbon and nitrogen in samples was calculated by comparison with certified standards and isotopic signatures are reported relative to the primary standard Vienna Pee Dee Belemnite scale. Photosynthetic nitrogen use efficiency (PNUE) was defined as the ratio of photosynthesis to leaf N content on a mass basis.

## Chlorophyll content

Prior to gas exchange, samples of selected fresh foliar tissue were analyzed for chlorophyll content, with a CCM-300 portable chlorophyll meter (Opti-Sciences, NH, USA)  A composite (n=3) of single point chlorophyll content (mg m^-2^) readings over 3mm diameter circles across each pinnae were measured.

# Results

Below are the boxplots (excluding outliers) for physiological measurements, including; photosynthesis (A~n~), stomatal conductance (g~s~), instantaneous water use efficiency (ITE), transpiration (E~l~) and chlorophyll content. Gas exchange was performed on a subset of individuals (n=10).

\

There is an issue with the gas exchange data from some fronds for individual #26 (2^nd^ and 3^rd^ year fronds). I have deleted it from physiology figures at the moment. I pasted the raw deleted data at the bottom so you can have a look.

\

```{r gas exchange, echo=FALSE}
par(mar=c(5,5,1,1))
boxplot(Photo ~ leafage, data=alldata_no26, ylab=photolab, ylim=c(0,5), col=frondcols2,outline=FALSE)

boxplot(Cond ~ leafage, data=alldata_no26[alldata_no26$Cond > 0 & alldata_no26$Cond < .45,], outline=FALSE, ylab=condlab,col=frondcols2, ylim=c(0, .5))

boxplot(Ci~leafage, data=alldata_no26[alldata_no26$Ci > 0,], ylab=cilab,col=frondcols2, outline=FALSE, ylim=c(300, 400))
```

\

```{r iwue, echo=FALSE}
par(mar=c(5,5,1,1))
boxplot(iwue ~ leafage, data=alldata_no26[alldata_no26$iwue > 0,], outline=FALSE, col=frondcols2, ylab=itelab)

boxplot(Trmmol ~ leafage, data=alldata_no26, outline=FALSE, col=frondcols,
        ylab=Elab)
```
Instantaneous water use efficiency looks like it declines in year 3,likely driven by transpiration instead of A~n~

\

```{r chl, echo=FALSE}
par(mar=c(5,5,1,1))
boxplot(chl ~ leafage, data=alldata, ylim=c(300, 700), col=frondcols2, outline=FALSE,ylab=chllab)

```

### Traits by leaf age

```{r phys, echo=FALSE}

par(mar=c(5,5,1,1))
boxplot(lma ~ leafage, data=alldata, ylab=lmalab, outline=FALSE,col=frondcols2)
boxplot(percN ~ leafage, data=alldata, ylim=c(0,4.5), outline=FALSE,ylab="Nitrogen content (%)", col=frondcols2)
boxplot(c13 ~ leafage, data=alldata, ylab=c13lab, col=frondcols2, outline=FALSE,ylim=c(-36.5, -32.5))

```

## Bivariate relationships

```{r bivar, echo=FALSE}
par(mar=c(5,5,1,1))
plot(Photo ~ percN, data=alldata, pch=21, bg=frondcols[as.factor(frond_age)], 
     cex=1.5, ylim=c(0, 6), xlim=c(0, 5), ylab=photolab, xlab="Nitrogen content  (%)")
legend("topleft", legend=yearsold, pt.bg=frondcols, pch=21, bty='n')

plot(amass ~ nmass, data=alldata_no26, pch=21, bg=frondcols[as.factor(frond_age)], cex=1.5, ylab=amasslab, xlab=nmasslab, ylim=c(0, 160), xlim=c(0, 50))
legend("topright", legend=yearsold, pt.bg=frondcols, pch=21, bty='n')

plot(Photo ~ Cond, data=alldata_no26, pch=21, bg=frondcols[as.factor(frond_age)], ylim=c(0, 6), xlim=c(0, 1), cex=1.5, ylab=photolab, xlab=condlab)
legend("bottomright", legend=yearsold, pt.bg=frondcols, pch=21, bty='n')

plot(iwue ~c13, data=alldata_no26, pch=21, bg=frondcols[as.factor(frond_age)], ylim=c(0, 10), xlim=c(-36, -32), cex=1.5, ylab=itelab, xlab=c13lab)
legend("topleft", legend=yearsold, pt.bg=frondcols, pch=21, bty='n')

```


```{r pnue, echo=FALSE}
par(mar=c(5,5.5,1,1))
boxplot(amass/nmass ~ leafage, data=alldata_no26,col=frondcols2, outline=FALSE,ylab=nuelab)

```

### Transpiration data seems bad for certain ages for #26
```{r baddat,}
photo[photo$Indiv == 26, c("Indiv", "Photo", "Cond", "Trmmol", "Ci")] 
```


# Discussion

# Literature Cited
